Sparse Function-space Representation \\ of Neural Networks

### 2023-05-23 paper/main.tex
Minor

\par All neural network designs and related hyperparameters are set similarly to \citet{immer2021improving} for a fair comparison, for instance we train the $2$-layer MLPs with learning rate $0.001$ for $10000$ epochs, using the full dataset instead of batching. In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512 \}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} and \cref{tbl:uci-appendix-acc} for the complete NLPD and accuracy results. Our code implementation of the UCI experiments has been built on top of the code provided for \citet{immer2021improving}, using the \our methods provided in the supplementary material.

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Negative log predictive density (NLPD, lower better) for our \our method compared to a GP subset based method which discards most of the data. Even with a small $M$ our method is able to provide good results.} 
	\label{tbl:uci-appendix}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{2pt}
	\setlength{\tblw}{0.15\textwidth}

>>>>

All neural network designs and related hyperparameters are set similarly to \citet{immer2021improving} for a fair comparison, for instance we train the $2$-layer MLPs with learning rate $0.001$ for $10000$ epochs, using the full dataset instead of batching. In addition, we vary the subset size $M \in  \{16, 32, 64, 128, 256, 512 \}$ to observe the impact of sparseness on the predictive performance, see \cref{tbl:uci-appendix} and \cref{tbl:uci-appendix-acc} for the complete NLPD and accuracy results. Our code implementation of the UCI experiments has been built on top of the code provided for \citet{immer2021improving}, using the \our methods provided in the supplementary material.

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Complements \cref{tbl:uci} in the main paper: Negative log predictive density (NLPD, lower better) for our \our method compared to a GP subset based method which discards most of the data \cite{immer2021improving}. These UCI data sets (num.\ of points $N$, input dim.\ $D$, num.\ classes $C$) demonstrate that even with a small number $M$ of inducing points our method is able to capture good predictive densities.} 
	\label{tbl:uci-appendix}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{2pt}
	\setlength{\tblw}{0.25\textwidth}
